---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```
# command shift k -- html file pops up
#command+option+i do not put install.packages('dplyr') in Rmd file

## Loading packages

I need to load dplyr... seems like ...
```{r}
library(dplyr)
```
## Working with data
explore dplyr functionality:
```{r}
mtcars %>%    # unique symbol in dplyr
  select(mpg, cyl, disp, hp)
```
# command shift m -- pipe

## Group by and summarize
```{r}
mtcars %>% 
  group_by(cyl, am) %>% 
  summarise(mean_mpg = mean(mpg))
```
## Mutation: add new columns
```{r}
matcars <- mtcars %>% 
   mutate(mpg_wt = mpg / wt,
         wt = wt * 1000)
```
View(mtcars)
```{r}
mtcars$mpg_wt <- mtcars$mpg / mtcars$wt
```
View(mtcars) ##another way of adding a column
summary(mtcars)

## Visualization
```{r}
library(ggplot2)
ggplot(mtcars, aes(x = mpg, y = wt, color = cyl)) +
  geom_point(alpha = .5) +
  theme_minimal()
```
#install.packages("ggplot2") in console


#install.packages('DT') in console -- to search datatable
```{r}
DT::datatable(mtcars)
```





